---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# valet

<!-- badges: start -->
<!-- badges: end -->

This package provides an R client to the Bank of Canada's valet API.
It provide access to all of the API's functionality except its RSS feeds.
There are currently a few bugs in how it handles series groups, and some tests to develop and run.

## installation

You can install the development version of valet from [GitHub](https://github.com/) with:

``` {r}
install.packages("devtools")
devtools::install_github("runkelcorey/valet")
```

## basic usage

The core functions of `valet` are `get_series()` and `get_group()`.
These retrieve observations from series and series groups, subject to some date filters.
Here's an example of the last five Canadian dollar--US dollar exchange-rate observations.

``` {r}
library(valet)
get_series("FXCADUSD", recent = 5)
```

## workflow

1. Suppose a researcher wanted to see what datasets the Bank of Canada offered:

```{r}
datasets <- get_list("groups")
```

This can be overwhelming, but it does allow us to filter. Let's look for monthly Canadian Effective Exchange Rates:
```{r}
subset(datasets, grepl("CEER", label))
```

We have two potential datasets, and the option to choose real or nominal data.
Let's take a look at their details before we grab what could be thousands of observations (in this case, let's say we're more interested in their comparisons against non-US major currencies than that they be nominal or real):^[It's important to note that `get_details` and `valet` make a distinction between grouped observations and single series.
The user must select `group = TRUE` or valet will not return a dataset.]
```{r}
get_details("CEER_MONTHLY_REAL", group = T)
get_details("CEER_MONTHLY_NOMINAL", group = T)
```

Both datasets satisfy this condition, so we'll grab the real data.

2. Download selected data
```{r}
get_group("CEER_MONTHLY_REAL")
```


3. You can grab a bunch of observations with a map-reduce framework, or leverage the Bank of Canada's own, comma-separated querying feature:

```{r}
get_list("series") %>%
  subset(grepl("NOON", label)) %>%
  .$name %>%
  paste0(collapse = ",") %>%
  get_series()
```

## also
The Bank of Canada's API documentation explains API usage thoroughly.
Their [website](https://www.bankofcanada.ca/) is useful for finding series too.
